%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelance Developer} % Job title
    {Fiverr} % Organization
    {Toronto, Ontario} % Location
    {May 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consulted with potential clients by providing proposals and designed solutions to fit their business needs}
        \item {Decreased onboarding time by implementing an intuitive web app to replace current Excel process}
        \item {Designed Dashboards and provided analytics using SQL and API microservices to retreive and display critical information}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {BluRoot Inc.} % Organization
    {Toronto, Ontario} % Location
    {Mar. 2017 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained a positive relationship with clients by designing solutions tailored to their needs.}
        \item {Reduced data entry for The Streaming Network by 100\% using API microservices in Node.js, Koa, and AWS EC2.}
        \item {Increased customer retention by implementing a RESTful API server for Texting in Zoho CRM (Twilio)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Support Analyst} % Job title
    {Enercare Inc.} % Organization
    {Markham, Ontario} % Location
    {May 2015 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and supported the AirWatch EMM solution across all technicians in Ontario}
        \item {Decreased the workload for the accounting team by automating dashboards for the billing process}
        \item {Used VBA to reduce data overage by automating warning emails to employees}
      \end{cvitems}
    }
\end{cventries}
